Signatures and Induction Principles for Higher Inductive-Inductive Types

### 2019-01-31 paper.tex
Add conf paper expansion note

@@

In summary, solutions for the strictness problems require significant deviation
from the approach of the current paper, of require significant further research.

@@

foobar

>>>>

The present paper is an expanded version of our conference paper \cite{hiit}.
In this version, we additionally compute notions of homomorphisms from
signatures, and compare them to logical relations, in Section
\ref{sec:morphisms}. We also explain a coherence problem in interpreting
syntaxes of type theories, and how this influenced the current paper, in Section
\ref{sec:coherence} and Section \ref{sec:categorical}.

@@

In summary, solutions for the strictness problems require significant deviation
from the approach of the current paper, or require significant further research.

@@
